\begin{center}
\thispagestyle{fancy}
\LARGE{\textbf{Acknowledgement}}
\end{center}
\linespread{1.33}
\large{\paragraph{}A project of such a vast coverage cannot be realized without help from numerous sources and people in the organization. We take this opportunity to express our gratitude to all those who have been helping us in making this project successful.}

\large{\paragraph{} We are highly indebted to our mentor \textbf{Dr. Mehul Maharishi}, HOD, Department of Computer Science and Engineering (AI), whose constant guidance, motivation and invaluable suggestions helped us navigate every challenge during the development of this system. We also extend our sincere thanks to our project coordinator \textbf{Mr. Manish Bharadwaj}, Assistant Professor, for his co-operation, encouragement, and critical remarks that directed our efforts in the right manner throughout the project lifecycle.}

\large{\paragraph{}We would also like to convey our sincere thanks to the faculty members of the Department of Computer Science and Engineering (AI) at Swami Keshvanand Institute of Technology, Management and Gramothan, Jaipur for their continuous support and guidance. Their academic inputs greatly contributed to the successful completion of this project.}

\large{\paragraph{}We are also grateful to the management of SKIT, Jaipur for providing the necessary infrastructure and resources that enabled us to work on this project effectively. Special thanks to our fellow classmates for their support and constructive feedback during the testing and review phases.}

\large{\paragraph{}Last but not least, we would like to thank all those who have directly or indirectly helped and cooperated in accomplishing this project.} \newline
\large{\textbf{Team Members}}:\\
Khushal Jangid (22ESKCA057)\\
Gaurav Pratap Singh (22ESKCA035)\\
Kapil Jarwal (22ESKCA054)\\
Himanshu Meena (22ESKCA047)\\
\newpage
