\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{99}

\bibitem{ref1}
I. Sommerville,
\textit{Software Engineering},
10th ed. Boston, MA, USA: Pearson, 2016.

\bibitem{ref2}
R. S. Pressman and B. R. Maxim,
\textit{Software Engineering: A Practitioner's Approach},
8th ed. New York, NY, USA: McGraw-Hill Education, 2014.

\bibitem{ref3}
Ministry of Housing and Urban Affairs, Government of India,
``Municipal Finances in India: A Study of Property Tax,''
\textit{National Institute of Urban Affairs Report},
New Delhi, India, 2021.

\bibitem{ref4}
S. Rajasekaran and G. A. Vijayalakshmi Pai,
\textit{Neural Networks, Fuzzy Logic, and Genetic Algorithms: Synthesis and Applications},
New Delhi, India: Prentice-Hall of India, 2010.

\bibitem{ref5}
Next.js Documentation,
``App Router -- Introduction,''
Vercel Inc., 2024. [Online].
Available: https://nextjs.org/docs

\bibitem{ref6}
Supabase Documentation,
``Supabase Auth and PostgreSQL,''
Supabase Inc., 2024. [Online].
Available: https://supabase.com/docs

\bibitem{ref7}
Razorpay,
``Razorpay Payment Integration Guide,''
Razorpay Software Pvt. Ltd., 2024. [Online].
Available: https://razorpay.com/docs

\bibitem{ref8}
Leaflet.js Documentation,
``Leaflet -- an open-source JavaScript library for mobile-friendly interactive maps,''
2024. [Online].
Available: https://leafletjs.com/reference.html

\bibitem{ref9}
Government of Rajasthan,
``District Level Circle (DLC) Rates -- Jaipur District,''
Stamps and Registration Department, Rajasthan, 2024.

\bibitem{ref10}
Ministry of Housing and Urban Affairs,
``Smart Cities Mission -- Digital Urban Governance Framework,''
Government of India, New Delhi, 2022.

\bibitem{ref11}
P. Ghosh and P. Bandyopadhyay,
``Digitization of Property Tax in Urban Local Bodies: Evidence from Indian Cities,''
\textit{Journal of Urban Economics and Management},
vol. 8, no. 2, pp. 45--62, 2022.

\bibitem{ref12}
T. H. Cormen, C. E. Leiserson, R. L. Rivest, and C. Stein,
\textit{Introduction to Algorithms},
3rd ed. Cambridge, MA, USA: MIT Press, 2009.

\end{thebibliography}
